### 2015-04-06 transactions.tex
Use correct class file for the camera ready version. Remove vertical space adjustments.
Formatting changes for camera-ready

\vspace{-1.5em}
\begin{smathpar}
\forall a,b,c.~\txn{a}{b,c} ~\wedge~ \sameobj{b}{c} ~\wedge~ \vis{b}{a}
\Rightarrow \vis{c}{a}
\end{smathpar}

@@

\vspace{-1.2em}
\begin{smathpar}
\begin{array}{l}
\cv_{tb} = \forall a:\rcf{getBalance}, b:\rcf{getBalance}, \\
\qquad (c:\rcf{withdraw} \vee \rcf{deposit}), (d:\rcf{withdraw} \vee \rcf{deposit}). \\
\qquad \txn{a,b}{c,d} ~\wedge~ \vis{c}{a} ~\wedge~ \sameobj{d}{b} \Rightarrow \vis{d}{b}
\end{array}
\end{smathpar}

@@

\begin{figure}
\vspace{-2.3mm}
\centering
\subfigure[Atomicity]{\label{fig:txn_atomicity}\includegraphics[width=0.25\columnwidth]{Figures/TxnAtomic}}
\hfill
\subfigure[Monotonic Atomic View]{\label{fig:txn_mav}\includegraphics[width=0.25\columnwidth]{Figures/TxnMAV}}
\hfill
\subfigure[Repeatable Read]{\label{fig:txn_rr}\includegraphics[width=0.25\columnwidth]{Figures/TxnRR}}
\caption{Semantics of transaction contracts. $x$ and $y$ are distinct objects.
The dotted line represents the visibility requested by the contracts.}
\label{fig:transaction}
\end{figure}

@@

\vspace{-1em}
\begin{smathpar}
\begin{array}{l}
\mavc = \forall a,b,c,d.~\txn{a,b}{c,d} ~\wedge~ \so{a}{b} ~\wedge~ \vis{c}{a} \\
\qquad\qquad\qquad\qquad ~\wedge~ \sameobj{d}{b} \Rightarrow \vis{d}{b}
\end{array}
\end{smathpar}

@@

\vspace{-1.2em}
\begin{smathpar}
\begin{array}{l}
\rrc = \forall a,b,c,d.~\txn{a,b}{c,d} ~\wedge~ \vis{c}{a} \\
\qquad\qquad\qquad\quad ~\wedge~ \sameobj{d}{b} \Rightarrow \vis{d}{b}
\end{array}
\end{smathpar}

>>>>

\vspace{-1em}
\begin{smathpar}
\forall a,b,c.~\txn{a}{b,c} ~\wedge~ \sameobj{b}{c} ~\wedge~ \vis{b}{a}
\Rightarrow \vis{c}{a}
\end{smathpar}

@@

\vspace{-1em}
\begin{smathpar}
\begin{array}{l}
\cv_{tb} = \forall a:\rcf{getBalance}, b:\rcf{getBalance}, \\
\qquad (c:\rcf{withdraw} \vee \rcf{deposit}), (d:\rcf{withdraw} \vee \rcf{deposit}). \\
\qquad \txn{a,b}{c,d} ~\wedge~ \vis{c}{a} ~\wedge~ \sameobj{d}{b} \Rightarrow \vis{d}{b}
\end{array}
\end{smathpar}

@@

\begin{figure}
\vspace{-2.3mm}
\centering
\subfigure[Atomicity]{
  \label{fig:txn_atomicity}
  \includegraphics[width=0.25\columnwidth]{Figures/TxnAtomic}
}
\hfill
\subfigure[Monotonic Atomic View]{
  \label{fig:txn_mav}
  \includegraphics[width=0.25\columnwidth] {Figures/TxnMAV}
}
\hfill
\subfigure[Repeatable Read]{
  \label{fig:txn_rr}
  \includegraphics[width=0.25\columnwidth]{Figures/TxnRR}
}
\caption{Semantics of transaction contracts. $x$ and $y$ are distinct objects.
The dotted line represents the visibility requested by the contracts.}
\label{fig:transaction}
\end{figure}

@@

\vspace{-0.6em}
\begin{smathpar}
\begin{array}{l}
\mavc = \forall a,b,c,d.~\txn{a,b}{c,d} ~\wedge~ \so{a}{b} ~\wedge~ \vis{c}{a} \\
\qquad\qquad\qquad\qquad ~\wedge~ \sameobj{d}{b} \Rightarrow \vis{d}{b}
\end{array}
\end{smathpar}

@@

\vspace{-0.6em}
\begin{smathpar}
\begin{array}{l}
\rrc = \forall a,b,c,d.~\txn{a,b}{c,d} ~\wedge~ \vis{c}{a} \\
\qquad\qquad\qquad\quad ~\wedge~ \sameobj{d}{b} \Rightarrow \vis{d}{b}
\end{array}
\end{smathpar}
